---
title: "Hello R"
author: "Justin Perez"
date: "Data 2401"
output: 
  html_document: 
    fig_width: 10
    fig_height: 6
    highlight: espresso
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT.

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

### Exercise 1

datasaurus_dozen rows: 1846 datasaurus_dozen variables: 3 datasaurus_dozen variable names: dataset, x, y

### Exercise 2

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Correlation coefficient for star dataset is larger than for dino dataset.

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

Correlation coefficient for circle dataset is larger than for dino dataset.

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))

```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)

```{r }
ggplot(datasaurus_dozen, aes(x=x, y=y, color=dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol=3)+
  theme(legend.position="none")

```

```{r }
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r=cor(x,y))
```
